---
title: "Prevailing Wage and Construction Accidents"
author: "Kaylie Abner"
date: "2025-12-01"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

- 421a/485x programs critical to workforce development and housing production in NYC
- Prevailing wage requirement for certain buildings in certain geographies part of recent iterations of the tax incentive

- Contested topic! 
- Want to examine an under-discussed aspect of prevailing wage: worker safety


## Research Question

Do the prevailing wage requirements in 485X and 421a(16) have any impact on construction injuries/fatalities?


## Datasources

- Construction Incidents:
-- Recent dataset available on OpenData 
-- This only goes back to 2024. 

 
## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Prevailing Wage Projects

```{r Potential Wages}
potential_485_x_bar_plot
```
## Projects on the edge of requiring Prevailing Wage

```{r split_wage_plot}
split_wage_plot
```

```{r Injuries}
potential_485_x_injuries_plot
```

